Automated Topic Naming

### 2012-01-17 ese/ese.tex
moved a paragraph
1. The reviewers would like to see discussion of the relationship of    the current draft and the previous MSR 2011 paper and more detailed    discussion of previous papers related to the current draft.    - [X] In intro provide more details    - [ ] In Previous work provide MORE details

Finally, in Ernst et al.~\cite{ernst10refsq}, we describe our earlier
project, similar to this, that identifies changes in quality requirements
in GNOME software projects; this approach was more exploratory, had
less validation, uses different word-lists, solely uses text-matching,
and does not leverage machine learning strategies. 
Hindle et al.~\cite{Hindle09ICSM} propose a windowed method of topic
analysis that we extend with labelled
topics, NFRs and new visualizations.

@@

@@

%\subsection{Timeline analysis}
Figures \ref{fig:mysql-timeline} and \ref{fig:maxdb-timeline} and \ref{fig:pgsql-timeline} show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
% based on the manually annotated
%topics, although this visualization can be generated from the
%results of labelled topic extraction.
There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to that NFR. 
For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with that NFR per period 
relative to the maximum number of labelled topics overall. 
For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs
\emph{functionality}, \emph{portability} and \emph{maintainability}
contain more labelled topics, since these NFRs have been more
intensely shaded; 
one interesting stream is \emph{efficiency} which shows periodic
activity, does this suggest that once maybe efficiency related changes
have longer lasting effects?
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.

>>>>

@@

Finally, 
this paper and our MSR 2011 paper~\cite{msr2011}, are based off of the
work of Ernst
et al.~\cite{ernst10refsq} and the work of Hindle et
al.~\cite{Hindle09ICSM}.
In Ernst et al.~\cite{ernst10refsq}, we describe our earlier
project, similar to this, that identifies changes in quality requirements
in GNOME software projects; this approach was more exploratory, had
less validation, uses different word-lists, solely uses text-matching,
and does not leverage machine learning strategies. 
This work, and our
MSR'2011 paper~\cite{msr2011}, extend this work by using 
word-lists to label extracted topics.
 Hindle et
al.~\cite{Hindle09ICSM}
 propose a windowed method of topic
analysis that we extend with labelled
topics, NFRs and new visualizations. This windowed method was
to bucket documents  by time windows (such as months), that could overlap if
necessary, and then use LDA to extract documents from these
bucket. These topics were then related to topics in other adjacent
buckets, and joined if deemed sufficiently similar. This work, and our
MSR'2011 paper~\cite{msr2011}, extend this method by labelling topics
and providing an alternative visualization, the topic time-line
described in Section \ref{sec:analysis}.

@@

%\subsection{Timeline analysis}
Topic time-lines are depicted in Figures \ref{fig:mysql-timeline} and
\ref{fig:maxdb-timeline} and \ref{fig:pgsql-timeline}. These topic time-lines show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
% based on the manually annotated
%topics, although this visualization can be generated from the
%results of labelled topic extraction.
There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to that NFR. 
For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with that NFR per period 
relative to the maximum number of labelled topics overall. 
For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs
\emph{functionality}, \emph{portability} and \emph{maintainability}
contain more labelled topics, since these NFRs have been more
intensely shaded; 
one interesting stream is \emph{efficiency} which shows periodic
activity, does this suggest that once maybe efficiency related changes
have longer lasting effects?
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.
